\section{Advantages and Disadvantages of Auro}
\subsection*{Advantages}
The main advantage of our project is that we have developed a personal assistant for the users.

\begin{enumerate}

\item We can make use of this project in many areas of work such as educational field, medical field.
\item We could make our searching operations more faster and easier.
\item This project gives us a simpler & user- friendly system that acts as a question-answering system

\end{enumerate}

\subsection*{Disadvantages}
The main disadvantage of our project is that we have developed a personal assistant that can accept text in English language only.
Some of the other disadvantages are listed below:
\begin{enumerate}

\item It can only accept text inputs and not voice or gestures as inputs.

\item Proper checking should be done to ensure that the queries are answered in a right way or else it can be a inconvenience to the user.

\item Proper internet connection is required for efficient operation of the system.

\item Auro is not fully trained to respond to 100\% correct answer.

\end{enumerate}

\section{Future Scope}
Some of the main future scope is that this project can be further extended to one which can accept voice and gestures as inputs along with text in another languages as well. In this way this project can become a good help for the users especially the disabled ones and people who are not familiar with English language.

Also this project can be again extended to level in which we can upload images through the user interface window and image searches can be done which can help users in an advanced way. One of future enhancement refers to the modification or improvements to the currently developed system. System enhancement may be required if there is change in organizational requirements of the user priorities. To carry out these changes the system have to be revaluated,programs need to be modified and then again tested for user acceptance.Future developements can be easily integrated to the system.