\section{Problem defenition}
In the current system, required answers to the questions are obtained by accessing web browsers and searching several websites which is time - consuming. The proposed system Auro is a solution to this problem which provide the answers in just a single step and thereby reducing the wastage of time.
\section{Objective}
The main objective of our proposed project is to build a simple personal assistant which is able to accept commands in the form of text (natural language: English) and respond back again in text (natural language). This project is implemented by Machine Learning (ML) and Natural Language Processing (NLP).  

\section{Scope}
The scope of this product is to provide an efficient and enhanced tool for the users to perform various operations quickly and more efficiently.  It finds application in many fields such as medical, educational etc.  This project is actually a demonstration of Machine learning and Natural Language Processing.  The main objective of the proposed system is to convert machines to user friendly devices through the use the use of Machine Learning and Natural Language processing.

\section{Introduction to the project}
We would have wished to use a single program just to get the answers in one go.  But what we do nowadays is that we have to scroll through different applications or different websites and search hard to get what we actually want.  The proposed system is a solution to this problem.  The project is to build a Personal Digital Assistant which is able to accept queries in the form of text (English) and respond back accordingly.  This application can be used to get or fetch the user required processes based on the input provided.  This document is intended for both the stakeholders and the developers of the software and will be proposed to the committee for its approval.